---
title: "April 19 Markdown Assignment"
author: "Evan LaPorte"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(janitor)
library(glue)
library(plotly)
library(DT)
library(kableExtra)
library(leaflet)
library(RColorBrewer)
library(htmlwidgets)
library(htmltools)
library(tigris)
library(scales)
options(tigris_class = "sf")

cfpb_complaints <- readRDS(url("https://github.com/Evan-712/April-19-Assignment/blob/main/complaints.rds?raw=true"))

```



```{r}
commonproducts <- cfpb_complaints %>% 
  group_by(product)

count(commonproducts) %>%
  arrange(desc(n))
  
```

As seen with this data, the most common products with complaints, by far, are those classified under "Credit reporting, credit repair services, or other personal consumer reports" with 255,748 complaints. The next two categories, "Debt collection" (46,088), "Credit card or prepaid card" (29,128), and "Mortgage" (20,940) don't have close to as many complaints. With such a significant extrapolation from this data, it is vital to investigate this sector further.

```{r}
Credit_Repair_Complaints <- cfpb_complaints %>% 
  filter(product == "Credit card or prepaid card") %>%
  group_by(sub_product)

count(Credit_Repair_Complaints) %>%
  arrange(desc(n))
```

Dissecting this data further, we can see how consumer complaints most commonly result from complaints over their "general-purpose credit card or charge card," in other words, standard credit cards. The prominence of complaints in this category, again, factor into more complaints than the other sub-product categories combined at 20,329 complaints, though there are significant complaints with the use of store credit cards (3,853), government benefit cards (3357), and general-purpose prepaid cards (1,388).

```{r}
Credit_Card_Violators <- cfpb_complaints %>%
  filter(product == "Credit card or prepaid card") %>%
  group_by(company)

count(Credit_Card_Violators) %>%
  arrange(desc(n))

```

Compared with other analysis this far, there is no discernible outlier within this data, with five companies (Citibank, Capital One Financial Corporation, JPMorgan Chase & Co., Bank of America, and Synchrony Financial) receiving over 2,000 complaints and nine other companies (U.S. Bancorp, American Express Company, Alliance Data Card Services, Discover Bank, Barclay's Bank, Xerox, Wells Fargo & Company, Comerica, and TD Bank) receiving over 500 complaints from consumers each.

